\LARGE How coexistence mechanisms mediate temporal stability

### 2014-11-12 manuscript/ms_CoexistStability.Rnw
changed mean resource supply to 100
small update
new script for relative nonlin

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{"SemiDiscreteModel"}
\caption{Schematic of our semi-discrete consumer-resource model. See text for parameter definitions.}
 \label{fig:model}
\end{figure}

@@

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{"CV_TwoPanel"}
\caption{Preliminary results from model simulations under storage effect conditions.}
 \label{fig:storeEffSims}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{"ConceptFig"}
\caption{Schematic of our semi-discrete consumer-resource model. See text for parameter definitions.}
 \label{fig:model}
\end{figure}

@@

\subsection{Implementing relative nonlinearity}
When considering consumer-resource dynamics, species coexistence by relative nonlinearity requires that each species has different nonlinear responses to resource availability, and resource availability must fluctuate through time. In a constant resource environment, the species with the lowest R* will always exclude the other species.

\begin{figure}
\begin{center}
<<echo=FALSE, fig=TRUE,jpeg=TRUE,height=3, width=8.5 >>=
source("../modelCode/continuousRelativeNonlinearity_CR.R")
@
\end{center}
\caption{Example time-series from our pulsed consumer-resource model where $g_{1,2}=1$, but species have different nonlinear uptake rate responses to resource supply (A). Species 2 has the lowest R* but its resource response saturates at a lower level than species 2. Species 1 is orange, species 2 is purple. The far right panel shows the population, by species, and community-level coefficient of variation.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth]{"CV_FourPanel"}
\caption{Preliminary results from model simulations under storage effect conditions.}
 \label{fig:storeEffSims}
\end{figure}

### 2014-11-12 manuscript/ms_CoexistStability.tex
changed mean resource supply to 100
small update
new script for relative nonlin

>>>>

\subsection{Implementing relative nonlinearity}
When considering consumer-resource dynamics, species coexistence by relative nonlinearity requires that each species has different nonlinear responses to resource availability, and resource availability must fluctuate through time. In a constant resource environment, the species with the lowest R* will always exclude the other species.

\begin{figure}
\begin{center}
\includegraphics{Fig-002}
\end{center}
\caption{Example time-series from our pulsed consumer-resource model where $g_{1,2}=1$, but species have different nonlinear uptake rate responses to resource supply (A). Species 2 has the lowest R* but its resource response saturates at a lower level than species 2. Species 1 is orange, species 2 is purple. The far right panel shows the population, by species, and community-level coefficient of variation.}
\end{figure}
